Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-15 presentation/presentation.tex
Last minute changes

    \only<8,10> {
      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=8cm]{../figures/example-dist-2.pdf}
      \end{textblock*}
    }

@@

    \only<11-13>{
    \vspace{0.55cm}
      \begin{itemize}
        \item \textbf{Dominating set}: all vertices outside of the set must have distance 1 to some vertex within the set.
        \vfill
        \only<11>{\item<7> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<12>{\item<12> Example: $\{2, 5\}$}
        \only<13>{\item<13> Example: $\{2, 4\}$}
      \end{itemize}
    }

@@

    \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
      \centering
      \includegraphics[width=6.5cm]{../figures/example-cfcp.pdf}
    \end{textblock*}

    \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
      \centering
      \includegraphics[width=6.5cm]{../figures/example-vcp.pdf}
    \end{textblock*}

@@

      \item \textbf{Cellular networks}: consist of base-stations and clients.
      \pause
      \item The problem: \textbf{frequency assignment}.

@@

    \begin{itemize}
      \item Our goal is to assign frequencies such that:
      \pause
      \begin{itemize}
        \item[(1)] Every client is served by a base-station with a unique frequency.
        \pause
        \item[(2)] Minimize the number of frequencies used.
      \end{itemize}
    \end{itemize}

@@

      \only<4>{
        \begin{textblock*}{14cm}(1cm, 3.5cm) % {block width} (coords)
          \begin{theorem}
          A graph cannot be conflict-free colored with $k$ colors if it contains a complete graph of $k+2$ vertices or a tattered graph of $k+3$ vertices.
          \end{theorem}
        \end{textblock*}
      }
    \end{textblock*}

>>>>

    \only<8> {
      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=8cm]{../figures/example-dist-2.pdf}
      \end{textblock*}
    }

    \only<10> {
      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=8cm]{../figures/example-d3s.pdf}
      \end{textblock*}
    }

@@

    \only<11-13>{
    \vspace{0.55cm}
      \begin{itemize}
        \item \textbf{Dominating set}: all vertices not in the set must have distance 1 to some vertex within the set.
        \vfill
        \only<11>{\item<7> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<12>{\item<12> Example: $\{2, 5\}$}
        \only<13>{\item<13> Example: $\{2, 4\}$}
      \end{itemize}
    }

@@

    \only<1, 8->{
      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-cfcp.pdf}
      \end{textblock*}
    }

    \only<2>{
      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-cf-1.pdf}
      \end{textblock*}
    }

    \only<3>{
      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-cf-2.pdf}
      \end{textblock*}
    }

    \only<4>{
      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-cf-3.pdf}
      \end{textblock*}
    }

    \only<5>{
      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-cf-4.pdf}
      \end{textblock*}
    }

    \only<6>{
      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-cf-5.pdf}
      \end{textblock*}
    }

    \only<7>{
      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-cf-6.pdf}
      \end{textblock*}
    }

    \only<1-7>{
      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-vcp.pdf}
      \end{textblock*}
    }

    \only<8>{
      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-vcp-1.pdf}
      \end{textblock*}
    }

    \only<9>{
      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-vcp-2.pdf}
      \end{textblock*}
    }

    \only<10>{
      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-vcp-3.pdf}
      \end{textblock*}
    }

    \only<11>{
      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-vcp-4.pdf}
      \end{textblock*}
    }

    \only<12>{
      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-vcp-5.pdf}
      \end{textblock*}
    }

    \only<13>{
      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
        \centering
        \includegraphics[width=6.5cm]{../figures/example-vcp-6.pdf}
      \end{textblock*}
    }

@@

      \item \textbf{Cellular networks}: consist of towers and clients.
      \pause
      \item The problem: \textbf{frequency assignment}.

@@

    \begin{itemize}
      \item Our goal is to assign frequencies such that:
      \pause
      \begin{itemize}
        \item[(1)] Every client is served by a tower with a unique frequency.
        \pause
        \item[(2)] Minimize the number of frequencies used.
      \end{itemize}
    \end{itemize}

@@

      \only<4>{
        \begin{textblock*}{14cm}(1cm, 3.5cm) % {block width} (coords)
          \begin{theorem}
          A graph cannot be conflict-free colored with $k$ colors if it contains a complete graph of $k+2$ vertices or a tattered graph of $k+3$ vertices as a minor.
          \end{theorem}
        \end{textblock*}
      }
    \end{textblock*}
